The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-07 paper/sections/results.tex
added figures

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/stiffness_sparsity.pdf}
  \caption{\revise{Our stiffness matrices can be sparse, while the corresponding matrix has to be dense in the traditional Boundary Element Method \cite{ArtDefo1999}. 
  Sparsity of our stiffness matrix is primarily determined by weight sparsity (number of non-zero weights at a given quadrature point) and polynomial order. }}
  \label{fig:stiffness_sparsity}
\end{figure}

@@

We further demonstrate \emph{qualitative} convergence of SEM with respect to linear tetrahedral finite elements when increasing the number of patches in use.
In \reffig{convergence}, we compare the static configurations of identical cantilevered beams, simulated using a Neohookean constitutive model (Young's Modulus $=$ $0.001$ GPa, Poisson's Ratio $=$ $0.45$). 
We use SEM with quadratic polynomials for this test and observe that our SEM simulation, made of 24 independent NURBS patches, shows good agreement with FEM. Each subdivision of the NURBS beam enables more complicated kinematics, 
but very few surface elements are needed to produce compelling results.

@@

>>>>

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/scalability.pdf}
  \caption{\revise{As a more extreme example of the shape-aware property of our algorithm, we simulate a falling octopus, and observe the 8 limbs moving independently.}}
  \label{fig:scalability}
\end{figure}

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/stiffness_sparsity.pdf}
  \caption{\revise{Our stiffness matrices can be sparse, while the corresponding matrix has to be dense in the traditional Boundary Element Method \cite{ArtDefo1999}. 
  Sparsity of our stiffness matrix is primarily determined by weight sparsity (number of non-zero weights at a given quadrature point) and polynomial order. }}
\end{figure}

@@

We demonstrate \emph{qualitative} convergence of SEM with respect to linear tetrahedral finite elements when increasing the number of patches in use.
In \reffig{convergence}, we compare the static configurations of identical cantilevered beams, simulated using a Neohookean constitutive model (Young's Modulus $=$ $0.001$ GPa, Poisson's Ratio $=$ $0.45$). 
\revise{We further perform basic \emph{quantitative} comparison against FEM by measuring the maximum deflection of the beam as we increase the number of patches along the beam. In \reffig{plot_beam_deflection}, the maximum beam deflection of the SEM beams is reported as a percentage of the FEM beam's maximum deflection. The parameters of the experiment match that of the previous qualitative test.}

%\begin{wrapfigure}{l}{0.5\columnwidth}
%    	\includegraphics{figures/deflection.pdf}
%	\caption{\revise{Te maximum beam deflection, as a percentage of the FEM beam's maximum deflection, is shown to converge to the FEM result as we add more parts along the beam.}}
%	  \label{fig:plot_beam_deflection}
%\end{wrapfigure}
\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/deflection_full.pdf}
	\caption{\revise{Te maximum beam deflection, as a percentage of the FEM beam's maximum deflection, is shown to converge to the FEM result as we add more parts along the beam.}}
  \label{fig:plot_beam_deflection}
\end{figure}

We use SEM with quadratic polynomials for this test and observe that our SEM simulation, made of 24 independent NURBS patches, shows good agreement with FEM. Each subdivision of the NURBS beam enables more complicated kinematics, 
but very few surface elements are needed to produce compelling results.

@@

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/octopus.pdf}
  \caption{\revise{As a more extreme example of the shape-aware property of our algorithm, we simulate a falling octopus, and observe the 8 limbs moving independently. Self-collision is not accounted for here.}}
  \label{fig:octopus}
\end{figure}

\begin{figure}[h]
  \includegraphics[width=\columnwidth]{figures/beam_twist.pdf}
  \caption{\revise{With the left end of the beam held fixed, we show the result of rotating the right end of the 22 part beam up to 360 degrees.}}
  \label{fig:twist}
\end{figure}
